Digital Analysis of Paintings

### 2014-04-27 paper.tex
Add HOG paper details.

@@

>>>>

This research appears to be of very limited use, but when used within as a part
of a larger system could provide some very interesting analysis which could be
used to train classifiers to detect forgeries, etc. but this still has limited
scope.

@@

A method for analysing the texture over an image to to create a histogram which
contains the orientation of all the gradients over an image. This technique has
been applied to the field of human detection\cite{dalal05histograms}, but is
also useful when applied to the realm of digital analysis of artwork as well.

A lot of the methodology for human detection involves the normalisation and
classification, but does include some useful information about the practises of
generating histograms of edge-orientated gradients. The gradients are computed
using a variety of discrete derivative masks combined with degrees of Gaussian
smoothing, although the results show that Gaussian smoothing and larger masks
damage the performance.

Each pixel is then binned according to a weighted vote from the mask, then each
vote is accumulated into orientation bins in local regions, which could be
rectangular or radial.

These orientation bins were evenly spaced across $0-\pi$ unsigned bins or
$i-2\pi$ signed bins. This is significant to note an orientation $\theta$ below
$\pi$ is often thought of as equivalent to $\theta + \pi$ in image processing.

Normalisation is then applied to reduce the effects of local contrast and is
good for performance in the field of human detection. For artwork this may be
less useful as these features are of importance.

This research shows very good experimental results of large, popular data sets
and beats all of the existing techniques on false positives (although no data
for false negatives is shown).

Although this research does not directly relate to the field of digital
analysis of artwork, it has been used to generate some interesting
analysis\cite{brown13can} although not all of the technique was applied in that
research.

The use of this research is the ability to store orientation data in
histograms, which are very easy to process digitally.

In conclusion, this technique provides a powerful analysis technique and the
experimental results on several decent sized data sets to prove this. Although
not all of the technique is useful or applicable to the digital analysis of
paintings, the parts which are have been successfully used in research into
artwork.
